On the limitations of using quantum mechanics in a fixed background of a Schwarzschild black hole

### 2016-05-21 Draft_BH_shells.tex
Add files via upload

Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things. In particular we assume the environment can be described classically and the system we are describing behaves quantum mechanically. There are points where this assumption breaks down and we can see a clear example of this in terms of the interference pattern of a double slit experiment(DESCRIBE THE SITUATION INVOLVING THE DOUBLE SPLIT EXPERIMENT HERE). In this paper we analyse when this description of quantum mechanics in a classical background breaks down in the presence of a BH.

>>>>

%Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things. In particular we assume the environment can be described classically and the system we are describing behaves quantum mechanically. There are points where this assumption breaks down and we can see a clear example of this in terms of the interference pattern of a double slit experiment(DESCRIBE THE SITUATION INVOLVING THE DOUBLE SPLIT EXPERIMENT HERE). In this paper we analyse when this description of quantum mechanics in a classical background breaks down in the presence of a BH.
